Spin canonical rings of log stacky curves

### 2015-07-03 stacky_write_up/spin_cring.tex
fix a false statement about vzb log spin result

In particular, we bound the degrees of generators and relations of a
log spin canonical ring. Let
$\sx$ be a stacky curve with signature $\sigma = (g; e_1, \ldots,
e_r; \delta)$. The application of O'Dorney's work to log spin
canonical rings gives a weak bound in the case $g = 0$ in
terms of the least common multiples of the $e_i$'s \cite[Chapter 5]
{dorney:canonical}. In their treatment of log spin canonical
rings, Voight and Zureick-Brown bounded generator degrees by $3 \cdot \max(5, e_1, \ldots, e_r)$
and relation degrees by $3 \cdot \max(5, e_1, \ldots, e_r)$ when $\halfcan$ is effective
\cite[Corollary 10.4.6]{vzb:stacky}. \todo{Peter: Seems a bit misleading by misrepresenting VZB's work; in reality they found fairly tight bounds in the case they worked in. Robin: How? This solely talks about their work for the log spin canonical rings which is clearly NOT tight. They give a larger bound than us for a subset of the cases we check...}

@@

%The main theorem of this paper, Theorem ~\ref{thm:main}, combined
%with a lemma of Voight and Zureick-Brown \cite[Lemma 10.2.1]
%{vzb:stacky}, provides a statement on all rings of modular forms.
Together with a theorem from Voight and Zureick-Brown \cite
[Theorem 9.3.1]{vzb:stacky} 
%and \cite[Theorem 9.3.1]{vzb:stacky}, 
\todo{Peter: The paragraph used to be confusingly redundant.  I think I fixed it but read through the commented out stuff to make sure it says the correct thing. Robin: Why are you ignoring Lemma 10.2.1 as well as its connection to Kodaira--Spencer?}
we have the following application to
rings of modular forms. 
%Note that the lemma from Voight and Zureick-
%Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately
%from the classical work of Kodaira--Spencer
%\cite{kodaira-spencer:deformations}.

>>>>

In particular, we bound the degrees of generators and relations of a
log spin canonical ring. Let
$\sx$ be a stacky curve with signature $\sigma = (g; e_1, \ldots,
e_r; \delta)$. The application of O'Dorney's work to log spin
canonical rings gives a weak bound in the case $g = 0$ in
terms of the least common multiples of the $e_i$'s \cite[Chapter 5]
{dorney:canonical}. In their treatment of log spin canonical
rings, Voight and Zureick-Brown bounded generator degrees by $3 \cdot \max(e_1, \ldots, e_r)$
and relation degrees by $6 \cdot \max(e_1, \ldots, e_r)$ when $\halfcan$ is effective
\cite[Corollary 10.4.6]{vzb:stacky}. \todo{Peter: Seems a bit misleading by misrepresenting VZB's work; in reality they found fairly tight bounds in the case they worked in. Robin: How? This solely talks about their work for the log spin canonical rings which is clearly NOT tight. They give a larger bound than us for a subset of the cases we check...}

@@

%The main theorem of this paper, Theorem ~\ref{thm:main}, combined
%with a lemma of Voight and Zureick-Brown \cite[Lemma 10.2.1]
%{vzb:stacky}, provides a statement on all rings of modular forms.
Together with a theorem from Voight and Zureick-Brown \cite
[Theorem 9.3.1]{vzb:stacky} 
%and \cite[Theorem 9.3.1]{vzb:stacky}, 
\todo{Peter: The paragraph used to be confusingly redundant.  I think I fixed it but read through the commented out stuff to make sure it says the correct thing. Robin: Why are you ignoring Lemma 10.2.1 as well as its connection to Kodaira--Spencer? These are necessary.}
we have the following application to
rings of modular forms. 
%Note that the lemma from Voight and Zureick-
%Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately
%from the classical work of Kodaira--Spencer
%\cite{kodaira-spencer:deformations}.
